Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-04-11 ltx/BrainIDE.tex
made some little changes and TODOs in the paper

\author{Dean~R.~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Michael~Dewar,~\IEEEmembership{Member,~IEEE,}
        Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
        David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
        Anthony~N.~Burkitt,~\IEEEmembership{Member,~IEEE,}
        and~other~Bosses/Supervisors,~\IEEEmembership{Member,~IEEE.}% <-this % stops a space% <-this % stops a space

@@

\thanks{Manuscript received Month Day, Year; revised Month Day, Year.}}

@@

where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. The synaptic response kernel can be more elaborate, using rise and fall time constants, however, this simple form serves our purposes. Nonlocal interactions between cortical populations are described by	

@@

where $f$ is spiking rate of populations $\mathbf{r}'$, $w$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface. The term $u\left(\mathbf{r},t\right)$ represents a known external input. The connectivity kernel is typically a Mexican hat shape described by the sum of weighted Gaussian functions. The shape of the kernel is not a critical parameter for our methodology so we shall not define it until later to keep the derivation as general as possible.

@@

The average firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function

@@

Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. By combining Eqs.~\ref{SpikesToPotential} and \ref{RateBasedInteractions} we get the spatiotemporal model

@@

>>>>

\author{Dean~R.~Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Parham~Aram,~\IEEEmembership{Graduate Student Member,~IEEE,}
        Michael~Dewar}
        Kenneth~Scerri,~\IEEEmembership{Member,~IEEE,}
        Visakan~Kadirkamanathan,~\IEEEmembership{Member,~IEEE,}
        David~B.~Grayden,~\IEEEmembership{Member,~IEEE,}
        Anthony~N.~Burkitt,~\IEEEmembership{Member,~IEEE,}
        and~other~Bosses/Supervisors,~\IEEEmembership{Member,~IEEE.}% <-this % stops a space% <-this % stops a space

@@

\thanks{Manuscript received Month Day, Year; revised Month Day, Year.}

@@

where $\alpha=\tau^{-1}$ and $\tau$ is the synaptic time constant and $\eta(t)$ is the Heaviside step function. Nonlocal interactions between cortical populations are described by	

@@

where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel, and $\Omega$ is the spatial domain, representing a cortical sheet or surface. The term $u\left(\mathbf{r},t\right)$ represents a known external input. The connectivity kernel is typically a ``Mexican hat'' function \todo{which describes strong local activation, weak mid-range repression and weak long-range activation \cite{}}. The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data. 

@@

The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function

@@

%Even though we will model $v_0$ and $\nu_0$ as being homogeneous across the cortical sheet we will express it as being spatially dependant allowing for generality at this point. 
By substituting \ref{RateBasedInteractions} into \ref{SpikesToPotential}  we get the spatiotemporal model

@@

\todo{Is the above right? I can't think of any way to make $\frac{d}{dt} h(t) + \alpha h(t)$ equal to $\delta(t)$}
